Future climate resilience of the Great Barrier Reef

### 2025-05-09 paper/paper_draft.qmd
Add figures and captions for ACCESS-ESM1-5 to quarto

![Reef relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#fig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth width=`{julia} violin_width`}

@@

![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median cover – DHW correlation level for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median proportion of habitable area occupied for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#fig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}

@@

![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#fig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered within each management area. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}

@@

![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}

@@

![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#fig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}

@@

![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#fig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}

@@

![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median DHW – tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#fig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}

@@

![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#fig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}

@@

![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#fig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered across the Great Barrier Reef. The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040. The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040. The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}

@@

![Median depth for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}

![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}

![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median total cover – DHW correlation value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}

![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median occupied proportion value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}

![Mean DHW for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median DHW value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}

![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median DHW - tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}

![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels..](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}

>>>>

![Reef relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#fig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth width=`{julia} violin_width`}

@@

![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median cover – DHW correlation level for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median proportion of habitable area occupied for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#fig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}

@@

![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#fig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered within each management area. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}

@@

![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}

@@

![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#fig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}

@@

![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#fig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}

@@

![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median DHW – tolerance value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#fig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}

@@

![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#fig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}

@@

![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#fig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered across the Great Barrier Reef. The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040. The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040. The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}

@@

![Median depth for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}

![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}

![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median total cover – DHW correlation value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}

![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median occupied proportion value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}

![Mean DHW for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median DHW value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}

![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median DHW - tolerance value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}

![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}
